---
title: "p8105_hw5_zw2974"
author: "Zihan Wu"
date: "2023-11-08"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(viridis)
library(readr)
library(plotly)
library(broom)
library(purrr)
knitr::opts_chunk$set(
    echo = TRUE,
    warning = FALSE,
    fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 2
#### Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time

```{r}
data_all = tibble(filename = list.files("./data/"))
readcsv = function(csv, path="./data/"){
  paste(path,csv,sep="/") |> 
    read.csv()
}
data_df =
  data_all |> 
  mutate(raw_results = map(data_all$filename, readcsv)) |> 
  unnest(raw_results) |> 
  mutate(filename_wo_csv = map_chr(.x = filename, ~ unlist(str_split(.x, "\\.") )[[1]] ) ) |> 
  mutate(
    arm = map_chr(.x = filename_wo_csv, ~ unlist(str_split(.x, "_") )[[1]] )) |> 
  mutate(
    subject_id = map_chr(.x = filename_wo_csv, ~ unlist(str_split(.x, "_") )[[2]] ))
```

#### Spaghetti Plot
```{r}
pivot_longer =
  data_df |> 
  pivot_longer(week_1:week_8,
               names_to = "week",
               names_prefix = "week_",
               values_to = "value") |> 
  mutate(week = as.integer(week))
plot =
  pivot_longer |> 
  group_by(filename_wo_csv) |> 
  ggplot(aes(x = week, y = value, color = interaction(arm, subject_id))) +
    geom_line()
plot
```

The plot indicates that over the span of eight weeks, there is a consistent uptrend in the measurements for all individuals in the experimental arm. In contrast, a comparative analysis of the experimental and control groups reveals that those in the experimental arm exhibit a more pronounced positive progression over time.

## Problem 3
#### First test μ=0
```{r}
sim_mean_pvalue = function(mu, n = 30, sigma = 5) {
  sim_data = tibble(
    x = rnorm(n = 30, mean = mu, sd = sigma),
  )
  
  sim_data |>  
    t.test() |>  
    broom::tidy() |>  
    select(mu_hat = estimate, 
           p_value = p.value)
  
}

sim_results_df = 
  expand_grid(
    true_mean = 0,
    iter = 1:5000
  ) |> 
  mutate(
    estimate_df = map(true_mean, sim_mean_pvalue)
  ) |> 
  unnest(estimate_df)
```
#### Repeat for μ={1,2,3,4,5,6}
```{r}
sim_results_df = 
  expand_grid(
    true_mean = c(0, 1, 2, 3, 4, 5, 6),
    iter = 1:5000
  ) |> 
  mutate(
    estimate_df = map(true_mean, sim_mean_pvalue)
  ) |> 
  unnest(estimate_df) |> 
  select(-iter)
```

#### *Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.
#### *Make a plot showing the average estimate of μ̂ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ̂ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ̂ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?

```{r}
sim_results_df |> 
  filter(p_value < 0.05) |> 
  group_by(true_mean) |> 
  summarise(power = n()/5000) |> 
  ggplot(aes(x = true_mean, y = power)) +
  geom_line() +
  geom_point() +
  geom_smooth() +
  theme_minimal() +
  labs(title = "Power vs. True value of μ", x = "True value of μ", y = "The power of the test")
```

As we can see in the plot, the power increases as the effect size raises from 0 to 6.

```{r}
sim_results_df |>  
  group_by(true_mean) |> 
  summarise(est_mean = mean(mu_hat)) |> 
  ggplot(aes(x = true_mean, y = est_mean)) +
  geom_line() +
  geom_point() +
  geom_smooth() +
  labs(title = "The average estimate value of μ vs. True value of μ", x = "True value of μ", y = "The average estimate value of μ")
```

As we can see in the plot, the relationship between the average estimate value of μ and the true value of μ is positive correlated.

```{r}
sim_results_df |> 
  filter(p_value < 0.05) |> 
  group_by(true_mean) |> 
  summarise(est_mean = mean(mu_hat)) |> 
  ggplot(aes(x = true_mean, y = est_mean)) +
  geom_line() +
  geom_point() +
  geom_smooth() +
  theme_minimal() +
  labs(title = "The average estimate value of μ (p_value < 0.05) vs. True value of μ", x = "True value of μ", y = "The average estimate value of μ")
```

As we can see in the plot, the sample average of μ̂ across tests for which the null is rejected (p_value < 0.05) is not approximately equal to the true value of μ. So the null will be rejected under the confidence interval.








